---
title: "22100 - R for Bio Data Science"
subtitle : "GROUP 18  FINAL PROJECT "
author: "Group 18"
date: '2022-05-10'
output: 
  ioslides_presentation:
    widescreen: true
    incremental: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
<style>
  background: white;
</style>



## Introduction {.build}

- background of the dataset 
  - where does the dataset come from 
  - aim of the investigation

## Materials and Methods | Data cleansing

Alem will write his comments here

- raw data 
  - how to handle "NA"
  - missing values
- code
- clean data

## Materials and Methods | Data wrangling and visualisation 

Balkis will write her comments here 

- beautiful and meaningful plots
- explanantion of the plots

## Materials and Methods | Data modelling {.columns-2}
```{r}
acc_2

acc_3

acc_4
```
## Materials and Methods | Data modelling

```{r, fig.width = 10}
(plot_roc(roc1, roc2, title = "Just Plasma") + plot_roc(roc3, roc4, title = "Simple")) / 
  (plot_roc(roc5, roc6, title = "PancRISK without Plasma") + plot_roc(roc7, roc8, title = "PancRISK complete"))
```

## Results {.build}

Results from modelling

## Discussion {.build}

- What we see from the model Is there any difference between our model and the model from the paper? 
- Limitation of our model 
- Any further improvements?















## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

