---
title: "22100 - R for Bio Data Science"
subtitle : "GROUP 18  FINAL PROJECT "
author: "Group 18"
date: '2022-05-10'
output: 
  ioslides_presentation:
    widescreen: true
    incremental: false
---
<style>
slides > slide {
color: #515151;
}
</style>
## Materials and Methods | Introduction
- background of the dataset 
  - where does the dataset come from 
  - aim of the investigation

## Materials and Methods | Data cleansing: from csv to tsv, assigned NA as '' or 'NA'
<style> 
pre {font-size: 15px;}
</style>
```{r, eval=FALSE}
my_data_clean <- my_data %>% 
  as_tibble %>% 
  bind_cols %>% 
  mutate(diagnosis = case_when(diagnosis == 1 ~ "control",
                               diagnosis == 2 ~ "benign",
                               diagnosis == 3 ~ "malignant"),
         sex = case_when(sex == "F" ~ "Female",
                         sex == "M" ~ "Male"),
         patient_cohort = case_when(patient_cohort == "Cohort1" ~ "Cohort_1",
                                    patient_cohort == "Cohort2" ~ "Cohort_2"),
         sampling_country = case_when(sample_origin == "BPTB" ~ "United Kingdom",
                                      sample_origin == "UCL" ~ "United Kingdom",
                                      sample_origin == "LIV" ~ "United Kingdom",
                                      sample_origin == "ESP" ~ "Spain"),
         sample_id = gsub('^.', '', sample_id)) %>% 
  select(.,
         -sample_origin,
         -benign_sample_diagnosis)
```
## Materials and Methods | Data visualisation 

- beautiful and meaningful plots
- explanantion of the plots

## Materials and Methods | Data modelling

- 1:1 Training- and validation-set split
- Sepereate/Multinomial logistic regression
<br/><br/>
- Candidate 1: binary plasma CA19_9 (cutoff 37 U/ml)
- Cand. 2 (Old panel): REG1A, LYVE1, TFF1; corrected for age and creatinine
- Cand. 3 (without plasma): REG1B, LYVE1, TFF1; corrected for age and creatinine
- Cand. 4 (PancRISK): REG1B, LYVE1, TFF1 and binary plasma CA19_9; corrected for age and creatinine

## Materials and Methods | Data modelling {.columns-2}
<style>
slides > slide > hgroup + article {
margin-top: 0px;
}
table {
background-color: #f6f6f6;
margin-block-end: 20px;
}
</style>
```{r, echo = FALSE}
acc_1

acc_2

acc_3

acc_4
```
## Materials and Methods | Data modelling
<style>
slides > slide {
  background: linear-gradient(#ffffff, #ffffff 85%, #ffffff);
  background-color: white;
  }
  
p { 
  margin-top: 0px; 
  margin-left: 0px;
} 
</style>
```{r, fig.width = 12, fig.height = 5.2, echo = FALSE}
(plot_roc(roc1, roc2, 
          title = "Binary CA19_9",
          caption = "Used binary plasma CA19_9\nCorrected for age\nN = 390") + 
 plot_roc(roc9, roc10, 
          title = "PancRISK (Sep. regressions)",
          caption = "Used REG1B, LYVE1, TFF1 and binary plasma CA19_9\nCorrected for age and creatinine\nN = 590\nSeperate regressions for contrasts:\nControl vs. Benign and Benign vs. Malignant")) /
(plot_roc(roc5, roc6, 
          title = "PancRISK without Plasma",
          caption = "Used REG1B, LYVE1 and TFF1\ncorrected for age and creatinine\nN = 590") + 
 plot_roc(roc7, roc8, 
          title = "PancRISK (Multinomial)",
          caption = "Used REG1B, LYVE1, TFF1 and binary plasma CA19_9\nCorrected for age and creatinine\nN = 590\nMultinom regression contrast Control vs. Benign vs. Malignant"))
```

## Results

- Results from modelling

## Discussion

- What we see from the model Is there any difference between our model and the model from the paper? 
- Limitation of our model 
- Any further improvements?