---
title: "22100 - R for Bio Data Science"
subtitle : "GROUP 18  FINAL PROJECT "
author: "Group 18"
date: '2022-05-10'
output: 
  ioslides_presentation:
    widescreen: true
    incremental: false
---
<style>
slides > slide {
color: #515151;
}
</style>
## Materials and Methods | Introduction
- background of the dataset 
  - where does the dataset come from 
  - aim of the investigation

## Materials and Methods | Data cleansing: from csv to tsv, assigned NA as '' or 'NA'
<style> 
pre {font-size: 15px;}
</style>
```{r, eval=FALSE}
my_data_clean <- my_data %>% 
  as_tibble %>% 
  bind_cols %>% 
  mutate(diagnosis = case_when(diagnosis == 1 ~ "control",
                               diagnosis == 2 ~ "benign",
                               diagnosis == 3 ~ "malignant"),
         sex = case_when(sex == "F" ~ "Female",
                         sex == "M" ~ "Male"),
         patient_cohort = case_when(patient_cohort == "Cohort1" ~ "Cohort_1",
                                    patient_cohort == "Cohort2" ~ "Cohort_2"),
         sampling_country = case_when(sample_origin == "BPTB" ~ "United Kingdom",
                                      sample_origin == "UCL" ~ "United Kingdom",
                                      sample_origin == "LIV" ~ "United Kingdom",
                                      sample_origin == "ESP" ~ "Spain"),
         sample_id = gsub('^.', '', sample_id)) %>% 
  select(.,
         -sample_origin,
         -benign_sample_diagnosis)
```
## Modelling 

<style>
slides > slide {
  background: linear-gradient(#ffffff, #ffffff 85%, #ffffff);
  background-color: white;
  }
img { 
 margin-top: -90px; 
  margin-left: 50px;
} 
</style>
 
<font size="2"> PCA and K-means  
</font>


```{r, fig.width = 8.5, fig.height = 6, echo = FALSE}


layout <- '
AB
'
patchwork <- wrap_plots(A=Data_onto_PCA_plot ,
           B=cumulative_variance_plot ,
           design = layout)
           

malignant_patchwork <-  wrap_plots(A=malignant_onto_PCA_plot ,
           B=malignant_cumulative_variance_plot ,
           design = layout)
  

patchwork<-patchwork + plot_annotation(
  title = "PCA results " ,
  subtitle = "The first two PCs can discriminate between patients suffering from PC from the control and benign diagnosed ones  ",
  caption= "Data from Silvana Debernardi et al" )& 
  theme(legend.position = 'bottom',
        plot.subtitle =  element_text(size=4),
        plot.title = element_text(size=8))

malignant_patchwork<- malignant_patchwork + plot_annotation(
  title = "PCA results " ,
  subtitle = "The first two PCs can't really discriminate between the 4 PDAC stages ",
  caption= "Data from Silvana Debernardi et al" )& 
  theme(legend.position = 'bottom',
        plot.subtitle =  element_text(size=4),
        plot.title = element_text(size=8))





patchwork_diagnosis_1 <-  (pl1|plasma_CA19_9_alone_plot) +
  #plot_layout(guides = 'collect')+ 
  plot_annotation(
  title = "K-means results " )&
  theme(legend.position = "bottom")

patchwork_diagnosis_2 <-(biomarkers_only_plot|complete_model_plot)+ 
  #plot_layout(guides = 'collect') + 
  plot_annotation(
  caption= "Data from Silvana Debernardi et al" )&
  theme(legend.position = "bottom")




top_patchwork <-  wrap_plots(A=patchwork ,
           B=patchwork_diagnosis_1 )
           #design = layout)
  
bottom_patchwork <-  wrap_plots(A=malignant_patchwork ,
           B=patchwork_diagnosis_2 )
           #design = layout)



top_patchwork/bottom_patchwork 


#layout <- '
#A#B
#C#D
#'

#wrap_plots(A=patchwork ,
           #B=patchwork_diagnosis_1 ,
           #C=malignant_patchwork,
           #D = patchwork_diagnosis_2, 
           #design = layout)


#patchwork_PCA<- (patchwork / malignant_patchwork)


#patchwork_PCA|patchwork_diagnosis


```


## Materials and Methods | Data modelling

- 1:1 Training- and validation-set split
- Sepereate/Multinomial logistic regression
<br/><br/>
- Candidate 1: binary plasma CA19_9 (cutoff 37 U/ml)
- Cand. 2 (Old panel): REG1A, LYVE1, TFF1; corrected for age and creatinine
- Cand. 3 (without plasma): REG1B, LYVE1, TFF1; corrected for age and creatinine
- Cand. 4 (PancRISK): REG1B, LYVE1, TFF1 and binary plasma CA19_9; corrected for age and creatinine

## Materials and Methods | Data modelling
<style>
slides > slide {
  background: linear-gradient(#ffffff, #ffffff 85%, #ffffff);
  background-color: white;
  }
  
p { 
  margin-top: 0px; 
  margin-left: 0px;
} 
</style>
```{r, fig.width = 12, fig.height = 5.2, echo = FALSE}
(plot_roc(roc1, roc2, 
          title = "Binary CA19_9",
          caption = "Used binary plasma CA19_9\nCorrected for age\nN = 390") + 
 plot_roc(roc9, roc10, 
          title = "PancRISK (Sep. regressions)",
          caption = "Used REG1B, LYVE1, TFF1 and binary plasma CA19_9\nCorrected for age and creatinine\nN = 590\nSeperate regressions for contrasts:\nControl vs. Benign and Benign vs. Malignant")) /
(plot_roc(roc5, roc6, 
          title = "PancRISK without Plasma",
          caption = "Used REG1B, LYVE1 and TFF1\ncorrected for age and creatinine\nN = 590") + 
 plot_roc(roc7, roc8, 
          title = "PancRISK (Multinomial)",
          caption = "Used REG1B, LYVE1, TFF1 and binary plasma CA19_9\nCorrected for age and creatinine\nN = 590\nMultinom regression contrast Control vs. Benign vs. Malignant"))
```

## Results
```{r, fig.width = 6, fig.height = 6.3, echo = FALSE}
(patchwork + plot_annotation(
  title = "PCA results " ,
  subtitle = "The first two PCs can discriminate between patients suffering from PC from the control and benign diagnosed ones  ",
  caption= "Data from Silvana Debernardi et al" )& 
  theme(legend.position = 'bottom',
        plot.subtitle =  element_text(size=6),
        plot.title = element_text(size=10)))/
(malignant_patchwork + plot_annotation(
  title = "PCA results " ,
  subtitle = "The first two PCs can't really discriminate between the 4 PDAC stages ",
  caption= "Data from Silvana Debernardi et al" )& 
  theme(legend.position = 'bottom',
        plot.subtitle =  element_text(size=6),
        plot.title = element_text(size=10)))
```

- Results from modelling

## Discussion

- What we see from the model Is there any difference between our model and the model from the paper? 
- Limitation of our model 
- Any further improvements?