---
title: "22100 - R for Bio Data Science"
subtitle : "GROUP 18  FINAL PROJECT "
author: "Group 18"
date: '2022-05-10'
output: 
  ioslides_presentation:
    widescreen: true
    incremental: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
<style>
slides > slide {
color: #515151;
}
</style>
## Introduction {.build}

- background of the dataset 
  - where does the dataset come from 
  - aim of the investigation

## Materials and Methods | Data cleansing

Alem will write his comments here

- raw data 
  - how to handle "NA"
  - missing values
- code
- clean data

## Materials and Methods | Data wrangling and visualisation 

Balkis will write her comments here 

- beautiful and meaningful plots
- explanantion of the plots

## Materials and Methods | Data modelling
- 1:1 Training- and validation-set split
- Sepereate/Multinomial logistic regression
<br/><br/>
- Candidate 1: binary plasma CA19_9 (cutoff 37 U/ml)
- Cand. 2 (Old panel): REG1A, LYVE1, TFF1; corrected for age and creatinine
- Cand. 3 (without plasma): REG1B, LYVE1, TFF1; corrected for age and creatinine
- Cand. 4 (PancRISK): REG1B, LYVE1, TFF1 and binary plasma CA19_9; corrected for age and creatinine

## Materials and Methods | Data modelling {.columns-2}
<style>
slides > slide > hgroup + article {
margin-top: 0px;
}
table {
background-color: #f6f6f6;
margin-block-end: 20px;
}
</style>
```{r}
acc_1

acc_2

acc_3

acc_4
```
## Materials and Methods | Data modelling 
<style>
slides > slide {
  background: linear-gradient(#ffffff, #ffffff 85%, #ffffff);
  background-color: white;
  }
  
p { 
  margin-top: -50px; 
  margin-left: 0px;
} 
</style>

```{r, fig.width = 12, fig.height = 5.2}
(plot_roc(roc1, roc2, 
          title = "Binary CA19_9",
          caption = "Used binary plasma CA19_9\nCorrected for age\nN = 390") + 
 plot_roc(roc9, roc10, 
          title = "PancRISK (Sep. regressions)",
          caption = "Used REG1B, LYVE1, TFF1 and binary plasma CA19_9\nCorrected for age and creatinine\nN = 590\nSeperate regressions for contrasts:\nControl vs. Benign and Benign vs. Malignant")) /
(plot_roc(roc5, roc6, 
          title = "PancRISK without Plasma",
          caption = "Used REG1B, LYVE1 and TFF1\ncorrected for age and creatinine\nN = 590") + 
 plot_roc(roc7, roc8, 
          title = "PancRISK (Multinomial)",
          caption = "Used REG1B, LYVE1, TFF1 and binary plasma CA19_9\nCorrected for age and creatinine\nN = 590\nMultinom regression contrast Control vs. Benign vs. Malignant"))
```

## Results {.build}

Results from modelling

## Discussion {.build}

- What we see from the model Is there any difference between our model and the model from the paper? 
- Limitation of our model 
- Any further improvements?















## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

